---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your group name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one student name, group, and ID per line; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                      |
|                                                   | 1.  136304 - Certificate - Alika Kayembe                                                                                |
|                                                   |                                                                                                      |
|                                                   | 2.  134984 - Certificate - Kaguamere Nelson Kamau                                                                                |
|                                                   |                                                                                                      |
|                                                   | 3.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 4.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 5.  ID - Group - Name                                                                                |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   |       Certificate                                                                                               |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                              |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                             |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                          |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                           |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# \<Loading the Dataset\>

Describe the code chunk here:

```{r Your Second Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
student_performance <- read.csv("data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset - dataset.csv", header = FALSE,
                         stringsAsFactors = TRUE)
library(readr)
```

Describe the next code chunk here:

```{r Your Third Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE)
}
require("readr")

student_performance <- read_csv(
  "data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset - dataset.csv",
  col_types = cols(
    gender = col_factor(levels = c("1", "0")),
    regret_choosing_bi = col_factor(levels = c("1", "0")),
    motivator = col_factor(levels = c("1", "0")),
    paid_tuition = col_factor(levels = c("1", "0")),
    extra_curricular = col_factor(levels = c("1", "0")),
    read_content_before_lecture = col_factor(levels = c("1", "2", "3", "4", "5")),
    anticipate_test_questions = col_factor(levels = c("1", "2", "3", "4", "5")),
    health = col_factor(levels = c("1", "2", "3", "4", "5")),
    GRADE = col_factor(levels = c("A", "B", "C", "D", "E"))
  )
)
library(vroom)
dat <- vroom("data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset - dataset.csv", delim = ",")
problems(dat)

View(student_performance)
library(readr)
```

## \<Preview loaded dataset\>

```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
dim(student_performance)
sapply(student_performance, class)
library(readr)
```

# \<Identify the number of instances that belong to each class\>

Describe the code chunk here:

```{r Your Fifth Code Chunk}
student_performance_freq <- student_performance$gender
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$regret_choosing_bi
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$motivator
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$paid_tuition
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$extra_curricular
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$read_content_before_lecture
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$anticipate_test_questions
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$health
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)

student_performance_freq <- student_performance$GRADE
cbind(frequency = table(student_performance_freq),
      percentage = prop.table(table(student_performance_freq)) * 100)
library(readr)
```

## \<Calculate the mode\>

```{r Your Fourth Code Chunk}
student_performance_gender_mode <- names(table(student_performance$gender))[
  which(table(student_performance$gender) == max(table(student_performance$gender)))
]
print(student_performance_gender_mode)
library(readr)
```


## \<Measure the distribution of the data for each variable\>

```{r Your Fourth Code Chunk}
summary(student_performance)

numeric_columns <- student_performance [, sapply(student_performance, is.numeric)]


# The data type of "yield" should be double (not numeric) so that it can be
# calculated.
standard_deviation <- sapply(numeric_columns, sd)

print(standard_deviation)

library(readr)
```


## \<Measure the variance of each variable\>

```{r Your Fourth Code Chunk}
numeric_columns <- student_performance [, sapply(student_performance, is.numeric)]

variance <- sapply(numeric_columns, sd)

print(variance)

library(readr)
```


## \<Measure the kurtosis of each variable\>

```{r Your Fourth Code Chunk}
if (!is.element("e1071", installed.packages()[, 1])) {
  install.packages("e1071", dependencies = TRUE)
}
require("e1071")

numeric_columns <- student_performance[, sapply(student_performance, is.numeric)]
kurtosis_values <- sapply(numeric_columns, kurtosis, type = 2)
library(readr)
```


## \<Measure the skewness of each variable\>

```{r Your Fourth Code Chunk}
numeric_columns <- student_performance[, sapply(student_performance, is.numeric)]
skewness_values <- sapply(numeric_columns, skewness, type = 2)
library(readr)
```


## \<Measure the covariance between variables\>

```{r Your Fourth Code Chunk}
student_performance_cov <- cov(student_performance[, sapply(student_performance, is.numeric)])
View(student_performance_cov)
library(readr)
```


## \<Measure the correlation between variables\>

```{r Your Fourth Code Chunk}
student_performance_cor <- cor(student_performance[, sapply(student_performance, is.numeric)])
View(student_performance_cor)
library(readr)
```


## \<Perform ANOVA on the “student_performance” dataset\>

```{r Your Fourth Code Chunk}
# Dependent variable:	GRADE
# Independent variables:	gender, paid_tuition and regret_choosing_bi
logistic_model <- glm(regret_choosing_bi ~ GRADE, data = student_performance, family = "binomial")
summary(logistic_model)

student_performance$regret_choosing_bi <- as.numeric(student_performance$regret_choosing_bi)  # Convert to numeric
student_performance_one_way_anova <- aov(regret_choosing_bi ~ GRADE, data = student_performance)
summary(student_performance_one_way_anova)
library(readr)
```


## \<Create Histograms for Each Numeric Attribute\>

```{r Your Fourth Code Chunk}
student_performance <- as.numeric(unlist(student_performance))
hist(student_performance, main = names(student_performance))

#boxplotting graph code
student_performance <- as.numeric(unlist(student_performance))
boxplot(student_performance, main = names(student_performance))

#barplotting graph code
barplot(table(student_performance), main = names(student_performance))

library(readr)
```


## \Missmaps for missing data\>

```{r Your Fourth Code Chunk}
# Execute the following to create a map to identify the missing data in each
# dataset:
if (!is.element("Amelia", installed.packages()[, 1])) {
  install.packages("Amelia", dependencies = TRUE)
}
require("Amelia")
missmap(student_performance, col = c("red", "grey"), legend = TRUE)
library(readr)
```


## \<Create a Correlation Plot\>

```{r Your Fourth Code Chunk}
if (!is.element("corrplot", installed.packages()[, 1])) {
  install.packages("corrplot", dependencies = TRUE)
}
require("corrplot")
corrplot(cor(student_performance), method = "circle")
library(readr)
```


## \<Scatter plot\>

```{r Your Fourth Code Chunk}
pairs(student_performance)  ~  + GRADE

library(readr)
```

